---
title: "Helpers for building an R package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Helpers for building an R package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = 'center', 
  fig.dim = c(7, 7), 
  out.width = "50%"
)
#devtools::load_all()
library("oeli")
```

This vignette demonstrates helper functions for building an R package.

## Response to an input check

The `input_check_response()` function standardizes responses to input checks, ensuring consistency.

```{r, input_check_response, error = TRUE}
x <- "1"
y <- 1

### check is successful
input_check_response(
  check = checkmate::check_character(x),
  var_name = "x",
  error = TRUE
)

### standardized check response
input_check_response(
  check = checkmate::check_character(y),
  var_name = "y",
  error = TRUE
)
```

## Create a package logo

The `package_logo()` function makes it easy to create a very basic package logo. Setting `use_logo = TRUE` will run `usethis::use_logo()` to set up the logo for your package.

```{r, create logo}
package_logo(
  package_name = "package",
  brackets = TRUE,
  use_logo = FALSE
)
```
